### 2021-07-31 paper/paper_draft.tex
updates

There is a lot of day-to-day and hour-to-hour variability in how coal are offered into the market. Figure \ref{fig:synth_coal_2019}, which shows all of the 7pm merit orders (left panel), their synthetic equivalents, and the average synthetic merit order for the last year of our sample, provides a sense of the degree of variability in our sample. Similar variability exists in the offers of generation from other dispatchable sources.\footnote{See online graphical appendix, Figure A1, for a similar Figure for all dispatchable generating source types.} Figure \ref{fig:synth_coal_2019} shows the degree to which changes in total offered capacity would skew our results if we attempted to base our analysis on offered megawatts. Instead, ny using percentiles of offered capacity as our units of measure, we can more cleanly ask how different segments of the supply curve shift vertically in response to different events, while implicitly assuming that the total offered power available in the market in a given hour is independent of the carbon pricing policy on offer at the time.

@@

\subsection{Facility-level impacts}

\subsection{Impacts By Generator Type}

\subsection{Impacts By Generator Type}

\subsection{Market-wide impacts}

>>>>

There is a lot of day-to-day and hour-to-hour variability in how coal are offered into the market. Figure \ref{fig:synth_coal_2019}, which shows all of the 7pm merit orders (left panel) and their synthetic equivalents, along with the average synthetic merit order for the last year of our sample (right panel), provides a sense of the variability in our sample. Similar variability exists in the offers of generation from other dispatchable sources.\footnote{See online graphical appendix, Figure A1, for a similar Figure for all dispatchable generating source types.} Figure \ref{fig:synth_coal_2019} shows the degree to which changes in total offered capacity would skew our results if we attempted to base our analysis on offered megawatts. Instead, by using percentiles of offered capacity as our units of measure, we can more cleanly ask how different segments of the supply curve shift vertically in response to different events, while implicitly assuming that the total offered power available in the market in a given hour is independent of the carbon pricing policy on offer at the time.

@@

\subsection{Market-wide impacts}
The most general results derive from the analysis of the market as a whole. Here, we are calculating for each hour of our sample the supply curve of power offered into the market which we summarize using a step function with 15 points of support mapping offers at given percentiles of total power offers. At each of these points of support, we also track the marginal carbon pricing cost and marginal output-based allocation value along with other market and environmental variables. We find, as shown in Table X that...

\subsection{Impacts By Generator Type}
We know that different generator types tend to offer their power into the market in different ways, and so our most detailed results are based on a decomposition of the market-wide impacts into impacts by type of plant. Here, we find that...

\subsection{Impacts By Offer Control}
We can also use the data post-2013 to assess the degree to which different market participants might offer their power into the merit order and how they have passed through carbon policy values to power offers. We only use data after 2013 for this analysis because, prior to that time, the AESO did not provide offer control records along with their merit order data. The remains a sufficient sample, since we have three full years of data (2013-2015) in the initial \SGER pricing program, along with at least one full year under each of the altered policy regimes over which to assess changed in offers by different market participants.

PPA explanation...

Balancing Pool explanation...

Return of PPAs to the Balancing Pool

Declining ability to identify TransCanada impacts because of changes in resources.
